---
title: "MSDR Capstone - NOAA Earthquake Visualizations"
author: "Yaakov Miller"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Installation

Use the devtools package:

```{r eval = FALSE}
library(devtools)
install_github("ykv001/ykvdpcap")
library(ykvdpcap)
```

## Functions

This package includes the following functions

* eq_clean_data
* eq_create_label
* eq_data_read
* eq_location_clean
* eq_map
* eq_time
* geom_timeline
* geom_timeline_label

## Usage

### Data loading and cleaning

```{r , message=FALSE}
library(ggplot2)
library(leaflet)
library(lubridate)
library(dplyr)
library(readr)
library(stringr)

library(ykvdpcap)
data<-system.file('extdata','data.gz', package = 'ykvdpcap')

eq_data <- eq_data_read(data)
knitr::kable(head(eq_data[,1:7]))

eq_clean <- eq_data %>% eq_clean_data()
knitr::kable(head(eq_clean[,1:7]))

```

### Time Line

```{r , message=FALSE}
eq_clean %>%
dplyr::filter(COUNTRY == "USA" & lubridate::year(DATE) >= 2000) %>%
eq_time(size="EQ_PRIMARY",color="DEATHS")
```

### With Location Names
```{r , message=FALSE}
eq_clean %>%
dplyr::filter(COUNTRY == "USA" & lubridate::year(DATE) >= 2000) %>%
eq_time(size="EQ_PRIMARY",color="DEATHS",alpha=0.5,timeline_label=TRUE)
```

### 2 Countries

```{r , message=FALSE}
eq_clean %>%
dplyr::filter((COUNTRY=="USA" | COUNTRY=="MEXICO") & lubridate::year(DATE) >= 2000) %>%
eq_time(y="COUNTRY",color="DEATHS",alpha=0.5)
```

### 2 Countries With Location Names

```{r , message=FALSE}
eq_clean %>%
dplyr::filter((COUNTRY=="USA" | COUNTRY=="CHILE") & lubridate::year(DATE) >= 2000) %>%
eq_time(y="COUNTRY",color="DEATHS",alpha=0.5,timeline_label=TRUE)
```

### Interactive Map

```{r , message=FALSE}
eq_clean %>%
dplyr::filter(COUNTRY == "PERU" & lubridate::year(DATE) >= 2000) %>%
eq_map(annot_col = "DATE")
```


### Interactive Map with automated popup text

```{r , message=FALSE}
eq_clean %>%
dplyr::filter(COUNTRY == "ITALY" & lubridate::year(DATE) >= 2000) %>%
dplyr::mutate(popup_text = eq_create_label(.)) %>%
eq_map(annot_col = "popup_text")
```
